Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-06-11 Paper/paper.tex
Update Section 1

Several counter-arguments against a higher incidence of AGN at high
redshift have also been made. \citet{2017MNRAS.468.4691D} and
\citet{2018MNRAS.473.1416M} pointed out that an enhanced number
density of AGN at $z\sim 6$ can lead to a much earlier
\HeII\ reionization.  For instance, He~\textsc{ii} reionization is
complete at $z=4.5$ in the model of \citet{2015ApJ...813L...8M},
compared to $z=3$ in the standard scenario
\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization will also
result in higher IGM temperatures due to the associated photoheating.
\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
mean density is twice as much in AGN-dominated reionization models as
the standard models at $z=3.5$--$5$, in conflict with constraints from
the \lya forest.  This inconsistency could be avoided by postulating a
reduced escape fraction of \HeII-ionizing photons in AGN, but it is
difficult to reconcile this with a unit escape fraction of
hydrogen-ionizing photons that is required to explain the Ly$\alpha$
opacity fluctuations.  Further arguments against AGN-dominated
reionization have been presented by \citet{2016MNRAS.459.2299F}, who
analysed the simulations of metal-line absorbers at $z\sim 6$.
\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
hydrodynamical simulations AGN-dominated UV background results in too
many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
C~\textsc{ii} at $z\sim 6$.  (However, note that these simulations
assume a $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
\citep{2002ApJ...565..773T}, which somewhat harder than recent
measurements ($L_\nu\propto\nu^{-1.7}$) by
\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} found that,
relative to the the standard model \citep{2012ApJ...746..125H}, the
observed N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
measurements seem to require a harder and more intense $>4$~Ry
background.)  Finally, comparing the \citet{2015AA...578A..83G} sample
to X-ray-selected quasar data at $z=0$--$6$,
\citet{2017MNRAS.465.1915R} argued that the faint end of the AGN UV
luminosity function at $z\sim 6$ is probably shallower that that
reported by \citet{2015AA...578A..83G}.  \citet{2017MNRAS.465.1915R}
argue that the apparent contradiction with the results of
\citet{2015AA...578A..83G} could be explained by contamination from
the AGN host galaxies for faint AGN.

@@

A straightforward way towards a more robust understanding of AGN
contribution to reionization is to determine the evolution of the AGN
UV luminosity function.  However, many recent inferences of the
luminosity function suffer from inconsistencies arising from
inhomogeneous selection and mixing of AGN data.  This has resulted in
a large scatter in the inferred high-redshift hydrogen-ionizing AGN
emissivity between various recent studies.  For instance, there is an
order of magnitude scatter between various estimates of the
hydrogen-ionizing AGN emissivity at $z=5$--$6$
\citep{2011ApJ...728L..26G, 2012ApJ...755..169M, 2015AA...578A..83G,
  2018PASJ...70S..34A, 2018AJ....155..131M, 2018MNRAS.474.2904P,
  2017ApJ...847L..15O}.  Our aim in this paper is to address this
issue, by constructing an AGN sample with robust redshift and
completeness estimates and homogeneous assumptions of the cosmology
and intrinsic AGN spectrum.  We discuss our sample construction in
Section~\ref{sec:sample}.  Our derived luminosity functions are
presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
our inference of the AGN contribution to hydrogen and helium
reionization.  We summarise our findings in Section~\ref{sec:conc}.

>>>>

Several counter-arguments against a higher incidence of AGN at high
redshift have also been made. \citet{2017MNRAS.468.4691D} and
\citet{2018MNRAS.473.1416M} pointed out that an enhanced number
density of AGN at $z\sim 6$ can lead to a much earlier
\HeII\ reionization.  For instance, He~\textsc{ii} reionization is
complete at $z=4.5$ in the model of \citet{2015ApJ...813L...8M},
compared to $z=3$ in the standard scenario
\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization will also
result in higher IGM temperatures due to the associated photoheating.
\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
mean density is twice as much in AGN-dominated reionization models as
the standard models at $z=3.5$--$5$, in conflict with constraints from
the \lya forest.  This inconsistency could be avoided by postulating a
reduced escape fraction of \HeII-ionizing photons in AGN, but it is
difficult to reconcile this with a unit escape fraction of
hydrogen-ionizing photons that is required to explain the Ly$\alpha$
opacity fluctuations.  Further arguments against AGN-dominated
reionization have been presented by \citet{2016MNRAS.459.2299F}, who
analysed the simulations of metal-line absorbers at $z\sim 6$.
\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
hydrodynamical simulations AGN-dominated UV background results in too
many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
C~\textsc{ii} at $z\sim 6$.  (However, note that these simulations
assume a $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
\citep{2002ApJ...565..773T}, which somewhat harder than recent
measurements ($L_\nu\propto\nu^{-1.7}$) by
\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} found that,
relative to the the standard model \citep{2012ApJ...746..125H}, the
observed N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
measurements seem to require a harder and more intense $>4$~Ry
background.)  Finally, comparing the \citet{2015AA...578A..83G} sample
to X-ray-selected quasar data at $z=0$--$6$,
\citet{2017MNRAS.465.1915R} argued that the faint end of the AGN UV
luminosity function at $z\sim 6$ is probably shallower that that
reported by \citet{2015AA...578A..83G}.  \citet{2017MNRAS.465.1915R}
argue that the apparent contradiction with the results of
\citet{2015AA...578A..83G} could be explained by contamination from
the host galaxies for faint AGN.

@@

A straightforward way towards a more robust understanding of AGN
contribution to UV background is to determine the evolution of the AGN
UV luminosity function.  To this end, several estimates of the
luminosity function at various redshifts have been published in the
last decade \citep{2009A&A...507..781S, 2011ApJ...728L..26G,
  2012ApJ...755..169M, 2013ApJ...773...14R, 2013ApJ...768..105M,
  2015AA...578A..83G, 2016ApJ...833..222J, 2016ApJ...829...33Y,
  2017ApJ...847L..15O, 2018PASJ...70S..34A}.  However, many of these
inferences of the luminosity function suffer from inconsistencies
arising from inhomogeneous selection and mixing of AGN data.  Some of
the data sets analysed in these studies consist of photometric
samples, which is likely to increase sample contamination.  In some
studies, distinct data sets binned differently in redshift and
magnitudes were inhomogeneously combined.  Some authors imposed
restricted priors on parameters while fitting luminosity function
models, e.g., by fixing luminosity function slopes to certain values,
which may bias the result.  Finally, some studies arbitrarily excluded
certain data sets.  This has resulted in a large scatter in the
inferred high-redshift hydrogen-ionizing AGN emissivity between
various recent studies.  For instance, there is an order of magnitude
scatter between various estimates of the hydrogen-ionizing AGN
emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O}.  Our
aim in this paper is to address this issue, by constructing an AGN
sample with robust redshift and completeness estimates and homogeneous
assumptions of the cosmology and intrinsic AGN spectrum.  After
constructing such a sample, we derive the UV luminosity function of
AGN from redshift $z=0$--$7$ and estimate the AGN contribution to the
UV background.  We discuss our sample construction in
Section~\ref{sec:sample}.  Our derived luminosity functions are
presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
our inference of the AGN contribution to hydrogen and helium
reionization.  We summarise our findings in Section~\ref{sec:conc}.
